### 2018-01-25 doc/manuscript.Rmd
Added code DOI
include dplyr, rename chunk to setup

```{r load_data, message=FALSE, echo=FALSE}
devtools::load_all('.')
knitr::opts_chunk$set(echo = FALSE)
ds0yr <- project_data %>% 
    dplyr::filter(VN == 0)
```

@@

All analyses were performed using R `r getRversion()` [@Rbase], along with the R
packages geepack `r packageVersion('geepack')` for GEE [@Hoejsgaard2006a] and pls
`r packageVersion('pls')` for PLS. The R code and extra analyses for
this manuscript is available at {{code doi}}. Results were considered
statistically significant at p<0.05, after adjusting for multiple testing using
the Benjamini-Hochberg False Discovery Rate [@Benjamini1995a]. STROBE was used
as a guideline for reporting [@Vandenbroucke2007b].

>>>>

```{r setup, message=FALSE, echo=FALSE}
devtools::load_all('.')
library(dplyr)
knitr::opts_chunk$set(echo = FALSE)
ds0yr <- project_data %>% 
    filter(VN == 0)
```

@@

All analyses were performed using R `r getRversion()` [@Rbase], along with the R
packages geepack `r packageVersion('geepack')` for GEE [@Hoejsgaard2006a] and pls
`r packageVersion('pls')` for PLS. The R code and extra analyses for
this manuscript is available at https://doi.org/10.6084/m9.figshare.5143438. Results were considered
statistically significant at p<0.05, after adjusting for multiple testing using
the Benjamini-Hochberg False Discovery Rate [@Benjamini1995a]. STROBE was used
as a guideline for reporting [@Vandenbroucke2007b].
